Efficient and Adjustable Run-Time Monitoring Using Dataflow-Guided Filtering

### 2014-09-12 evaluation.tex
Add results for FPGA-based monitor.
Also filled in missing data for filtered/bc sweep.

>>>>

% Flex UMC sweep
\begin{figure*}
  \begin{center}
    \includegraphics[width=\linewidth]{figs/data_fpga_umc_sweep.pdf}
    \vspace{-0.2in}
    \caption{Coverage versus varying overhead budget for UMC running on an FPGA-based monitor.}
    \label{fig:evaluation.fpga_umc_sweep}
    \vspace{-0.1in}
  \end{center}
\end{figure*}

In addition to evaluating our system for a core-based monitor, we also
evaluated partial monitoring on a higher performance FPGA-based monitor. This
setup is based on the FlexCore \cite{flexcore-micro10} setup and uses a
fully-pipelined monitor running on an FPGA fabric at half the frequency of the
main core. We show results only for UMC. In this case, full overheads of
monitoring range from 10-70\%. Figure~\ref{fig:evaluation.fpga_umc_sweep} shows
the coverage achieved as we sweep overhead from 1-70\%. We see that partial
monitoring can allow the overheads of such a system to be pushed below 10\%
while still providing partial coverage.
